---
title: "MLR"
author: "Qi Yumeng"
date: "2023-12-07"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include = FALSE}
library(tidyverse)
library(tidymodels)
library(MASS)
library(corrplot)
```

```{r load_data, include = FALSE}
df_2013_raw =  read_csv("data/merge_data_2013.csv", show_col_types = FALSE)
df_2017_raw = read_csv("data/merge_data_2017.csv", show_col_types = FALSE)

df_2013_mlr = df_2013_raw |>
  mutate(if_delay = if_else(arr_delay >0,1,0),
         if_delay = factor(if_delay),
         #carrier_bin = if_else(!(carrier %in% c('UA','EV','DL','B6')),'Others',carrier),
         #month = factor(month,levels = 1:12, labels = month.abb[1:12]),
         arrival_date = paste(year,"-",month,"-",day, sep = ""),
         arrival_date = date(arrival_date)
         ) |>
  filter(!(dest %in% setdiff(unique(df_2013_raw$dest),unique(df_2017_raw$dest))),
         !(carrier %in% setdiff(unique(df_2013_raw$carrier),unique(df_2017_raw$carrier))))|>
  dplyr::select(-`...1`,-tailnum,-if_delay,
           -year, -month, -day) 
```

```{r scale}
df_2013_mlr = df_2013_mlr |>
  mutate_if(is.numeric, scale) 
# no correlation coefficient larger than 0.8
# so no need for deleting 
M = cor(df_2013_mlr |> select_if(is.numeric))
corrplot(M, order = 'AOE', type = 'upper', tl.pos = 'n', method = "number")
corrplot(M, add = TRUE, type = 'lower', method = 'ellipse', order = 'AOE',
         diag = FALSE, tl.pos = 'l', cl.pos = 'n',tl.col='black')
#corrplot(cor(df_2013_mlr |> select_if(is.numeric)),  method = "number")
# delete distance and wind_speed for less unqiue value

df_2013_mlr = df_2013_mlr |>
 dplyr::select(-wind_speed,-distance)
```


```{r AIC, include = FALSE}
#fit = lm(arr_delay ~ . , data = df_2013_mlr)
#stepAIC(fit, direction="both")
```

```{r estimate plot}
fit_AIC = lm(formula = arr_delay ~ origin + hour + carrier + flight + dest + 
    air_time + wind_dir + pressure + visib + arrival_date,
    data = df_2013_mlr)
#summary(fit_AIC)

#stargazer(fit_AIC, title="Regression Results",type='html', single.row = FALSE,  ci=TRUE)

coeff <- tidy(fit_AIC) %>% 
  arrange(desc(abs(estimate))) %>%
  filter(term != '(Intercept)') %>% 
  slice(1:20)
ggplot(coeff, 
       aes(x = reorder(term,estimate), y = estimate)) + geom_col() + coord_flip()+
  xlab('Predictors')+
  ylab('Estimate')+
  theme(legend.position = "none") + theme_minimal()

```
<table style="text-align:center"><caption><strong>Regression Results</strong></caption>
<tr><td colspan="2" style="border-bottom: 1px solid black"></td></tr><tr><td style="text-align:left"></td><td><em>Dependent variable:</em></td></tr>
<tr><td></td><td colspan="1" style="border-bottom: 1px solid black"></td></tr>
<tr><td style="text-align:left"></td><td>arr_delay</td></tr>
<tr><td colspan="2" style="border-bottom: 1px solid black"></td></tr><tr><td style="text-align:left">originJFK</td><td>-0.114<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-0.144, -0.085)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">originLGA</td><td>-0.056<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-0.081, -0.032)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">hour</td><td>0.167<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(0.159, 0.175)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">carrierAS</td><td>-0.258<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-0.446, -0.070)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">carrierB6</td><td>0.140<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(0.101, 0.180)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">carrierDL</td><td>-0.057<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-0.095, -0.018)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">carrierEV</td><td>0.292<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(0.224, 0.360)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">carrierF9</td><td>0.338<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(0.191, 0.485)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">carrierHA</td><td>-0.391<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-0.672, -0.110)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">carrierOO</td><td>0.078</td></tr>
<tr><td style="text-align:left"></td><td>(-0.753, 0.909)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">carrierUA</td><td>-0.006</td></tr>
<tr><td style="text-align:left"></td><td>(-0.044, 0.032)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">carrierVX</td><td>-0.046</td></tr>
<tr><td style="text-align:left"></td><td>(-0.116, 0.024)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">carrierWN</td><td>0.092<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(0.028, 0.156)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">flight</td><td>-0.045<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-0.066, -0.023)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destACK</td><td>3.736<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.194, 4.278)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destALB</td><td>3.963<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.502, 4.423)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destATL</td><td>2.717<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.309, 3.125)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destAUS</td><td>0.780<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(0.377, 1.184)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destAVL</td><td>2.946<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.461, 3.431)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destBDL</td><td>3.991<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.528, 4.454)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destBGR</td><td>3.407<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.940, 3.873)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destBHM</td><td>2.403<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(1.933, 2.874)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destBNA</td><td>2.585<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.173, 2.996)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destBOS</td><td>3.807<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.385, 4.228)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destBQN</td><td>1.139<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(0.706, 1.571)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destBTV</td><td>3.742<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.316, 4.168)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destBUF</td><td>3.631<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.209, 4.053)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destBUR</td><td>-1.432<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-1.886, -0.978)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destBWI</td><td>4.031<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.582, 4.480)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destCAE</td><td>3.092<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.545, 3.639)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destCHO</td><td>3.443<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.808, 4.078)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destCHS</td><td>2.925<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.508, 3.342)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destCLE</td><td>3.330<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.909, 3.750)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destCLT</td><td>3.290<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.873, 3.707)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destCMH</td><td>3.313<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.876, 3.750)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destCVG</td><td>3.045<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.627, 3.462)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destDAY</td><td>3.043<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.618, 3.468)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destDCA</td><td>3.995<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.565, 4.425)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destDEN</td><td>0.690<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(0.291, 1.088)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destDFW</td><td>1.013<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(0.613, 1.413)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destDSM</td><td>2.096<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(1.638, 2.554)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destDTW</td><td>3.084<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.670, 3.498)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destEGE</td><td>0.031</td></tr>
<tr><td style="text-align:left"></td><td>(-0.433, 0.495)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destFLL</td><td>1.989<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(1.587, 2.391)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destGRR</td><td>3.073<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.641, 3.505)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destGSO</td><td>3.318<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.893, 3.742)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destGSP</td><td>3.139<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.705, 3.574)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destHNL</td><td>-6.062<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-6.551, -5.574)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destHOU</td><td>0.990<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(0.583, 1.396)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destIAD</td><td>3.918<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.494, 4.341)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destIAH</td><td>1.154<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(0.755, 1.553)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destIND</td><td>2.872<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.449, 3.296)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destJAC</td><td>0.562</td></tr>
<tr><td style="text-align:left"></td><td>(-0.575, 1.700)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destJAX</td><td>2.521<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.108, 2.934)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destLAS</td><td>-0.781<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-1.181, -0.381)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destLAX</td><td>-1.232<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-1.632, -0.833)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destLGB</td><td>-1.398<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-1.824, -0.972)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destMCI</td><td>1.795<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(1.384, 2.206)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destMCO</td><td>2.232<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(1.829, 2.636)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destMDW</td><td>2.673<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.259, 3.087)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destMEM</td><td>2.110<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(1.699, 2.521)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destMHT</td><td>3.928<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.487, 4.369)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destMIA</td><td>1.920<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(1.517, 2.323)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destMKE</td><td>2.701<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.286, 3.115)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destMSN</td><td>2.522<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.095, 2.949)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destMSP</td><td>1.999<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(1.594, 2.404)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destMSY</td><td>1.584<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(1.179, 1.988)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destMVY</td><td>3.671<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.112, 4.231)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destMYR</td><td>2.914<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.173, 3.655)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destOAK</td><td>-1.810<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-2.277, -1.344)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destOMA</td><td>1.781<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(1.352, 2.211)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destORD</td><td>2.502<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.094, 2.909)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destORF</td><td>3.664<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.228, 4.101)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destPBI</td><td>2.092<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(1.688, 2.496)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destPDX</td><td>-1.353<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-1.770, -0.936)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destPHL</td><td>4.415<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.636, 5.193)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destPHX</td><td>-0.577<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-0.981, -0.174)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destPIT</td><td>3.570<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.142, 3.997)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destPSE</td><td>0.511<sup>**</sup></td></tr>
<tr><td style="text-align:left"></td><td>(0.026, 0.997)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destPSP</td><td>-1.201<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-2.056, -0.346)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destPVD</td><td>4.055<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.592, 4.518)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destPWM</td><td>3.887<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.461, 4.313)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destRDU</td><td>3.486<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.065, 3.908)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destRIC</td><td>3.756<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.330, 4.183)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destROC</td><td>3.723<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.297, 4.149)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destRSW</td><td>1.772<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(1.367, 2.176)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destSAN</td><td>-1.153<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-1.558, -0.748)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destSAT</td><td>0.522<sup>**</sup></td></tr>
<tr><td style="text-align:left"></td><td>(0.094, 0.951)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destSAV</td><td>2.820<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.393, 3.247)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destSBN</td><td>2.826<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(1.457, 4.195)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destSDF</td><td>2.896<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.464, 3.327)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destSEA</td><td>-1.226<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-1.632, -0.821)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destSFO</td><td>-1.436<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-1.838, -1.034)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destSJC</td><td>-1.653<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-2.119, -1.187)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destSJU</td><td>1.128<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(0.727, 1.529)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destSLC</td><td>-0.255</td></tr>
<tr><td style="text-align:left"></td><td>(-0.660, 0.149)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destSMF</td><td>-1.361<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-1.855, -0.867)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destSNA</td><td>-1.454<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-1.877, -1.032)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destSRQ</td><td>1.929<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(1.513, 2.344)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destSTL</td><td>2.275<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(1.868, 2.683)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destSTT</td><td>1.215<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(0.767, 1.664)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destSYR</td><td>3.839<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(3.406, 4.272)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destTPA</td><td>2.103<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(1.700, 2.507)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destTYS</td><td>3.414<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(2.925, 3.904)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">destXNA</td><td>1.878<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(1.375, 2.381)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">air_time</td><td>1.628<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(1.565, 1.691)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">wind_dir</td><td>-0.081<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-0.089, -0.073)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">pressure</td><td>-0.071<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-0.079, -0.063)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">visib</td><td>-0.107<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-0.115, -0.099)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">arrival_date</td><td>0.0001<sup>*</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-0.00001, 0.0001)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td style="text-align:left">Constant</td><td>-2.811<sup>***</sup></td></tr>
<tr><td style="text-align:left"></td><td>(-4.077, -1.546)</td></tr>
<tr><td style="text-align:left"></td><td></td></tr>
<tr><td colspan="2" style="border-bottom: 1px solid black"></td></tr><tr><td style="text-align:left">Observations</td><td>57,575</td></tr>
<tr><td style="text-align:left">R<sup>2</sup></td><td>0.113</td></tr>
<tr><td style="text-align:left">Adjusted R<sup>2</sup></td><td>0.112</td></tr>
<tr><td style="text-align:left">Residual Std. Error</td><td>0.943 (df = 57464)</td></tr>
<tr><td style="text-align:left">F Statistic</td><td>66.762<sup>***</sup> (df = 110; 57464)</td></tr>
<tr><td colspan="2" style="border-bottom: 1px solid black"></td></tr><tr><td style="text-align:left"><em>Note:</em></td><td style="text-align:right"><sup>*</sup>p<0.1; <sup>**</sup>p<0.05; <sup>***</sup>p<0.01</td></tr>
</table>